# How the metadata JSON could be done in R

To encapsulate the functionality of creating and saving metadata as a JSON file into a function in R, you can define a custom function that takes necessary parameters as inputs and follows the steps you've outlined. Here's how you can do it:

1. **Define the Function**: Create a function that accepts parameters for various metadata attributes like the dataset name, description, URL, etc.
2. **Set Default Values**: Optionally, provide default values for some parameters.
3. **Generate the Metadata List**: Inside the function, construct the metadata list using the provided parameters.
4. **Convert to JSON and Save**: Use `jsonlite` to convert the metadata to JSON and then save it to a file.

Here's an example of how this function might look:

```{r}
library(jsonlite)

createMetadataJSON <- function(dataset_name, dataset_description, dataset_url, creator_name, creator_email, date_published = Sys.Date(), license_url = "https://creativecommons.org/licenses/by/4.0/", json_filename = "metadata.json") {
  metadata <- list(
    "@context" = "http://schema.org",
    "@type" = "Dataset",
    "name" = dataset_name,
    "description" = dataset_description,
    "identifier" = dataset_url,
    "url" = dataset_url,
    "datePublished" = date_published,
    "creator" = list(
      "@type" = "Person",
      "name" = creator_name,
      "email" = creator_email
    ),
    "license" = license_url,
    "encodingFormat" = "text/csv"
  )

  writeLines(toJSON(metadata, pretty = TRUE), json_filename)
  return(json_filename)
}
```

To use this function, you would call it with the appropriate arguments. For example:

```{r}
json_file_name <- createMetadataJSON(
  dataset_name = "Cultural Employment Growth Data",
  dataset_description = "A dataset containing cultural employment growth data.",
  dataset_url = "https://example.com/datasets/cult_emp_growth_sex.csv",
  creator_name = "Your Name",
  creator_email = "your@email.com"
)
```

This function will create a JSON metadata file with the specified details and return the name of the JSON file created. You can adjust the parameters and the structure of the metadata as needed for your specific use case.
